Reasonably Programmable Literal Notation

### 2018-06-16 icfp18/syntax-icfp18.tex
more tightening of acks

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
   This work was
supported in part by AFRL and DARPA under agreement \#FA8750-16-2-0042;
 by the NSA under lablet contract \#H98230-14-C-0140; and by Ravi Chugh
 at the University of Chicago. The authors
would like to thank Robert Harper, Karl Crary and Eric Van Wyk for 
valuable feedback on the first author's doctoral dissertation, which forms the basis of this work; 
Charles Chamberlain, 
for his crucial contributions to the implementation and for valuable feedback on the
paper; and members of the PL Reading Group at University of Chicago, and the anonymous referees
at ICFP and at prior conferences, for their valuable critiques, which substantially improved the paper.

>>>>

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
   This work was
supported in part by AFRL and DARPA under agreement \#FA8750-16-2-0042;
 by the NSA under lablet contract \#H98230-14-C-0140; and by Ravi Chugh
 at the University of Chicago. The authors
would like to thank Robert Harper, Karl Crary and Eric Van Wyk for 
valuable feedback on the first author's doctoral dissertation, which forms the basis of this work; 
Charles Chamberlain, 
for his crucial contributions to the implementation and for valuable feedback on the
paper; and members of the PL Reading Group at University of Chicago, and the anonymous referees
at ICFP and prior conferences, for their valuable critiques, which substantially improved the paper.
